Unveiling Robustness Threats by Mining the Exception Stack Traces of over 600 Android Projects

### 2014-09-06 android-stacks.tex
square content

\noindent \fbox{ \begin{minipage}{0.96\columnwidth} \emph{
Approximately 52\% of the reported stack traces were associated to programming mistackes. 
And 27,71\% of all stack traces of reported a java.lang.NullPointerException the root cause.
}
\end{minipage}}

@@

\noindent \fbox{ \begin{minipage}{0.96\columnwidth} \emph{
An unexpected fragility was detected: a checked exception being thown by a native method and not declared  
on the ``exception interface" of such method and all methods on the invocation chain.
}
\end{minipage}}

@@

\noindent \fbox{ \begin{minipage}{0.96\columnwidth} \emph{
The cross-type wrappings show us that even if the developer sticks to Java
specification and best practices, it will be dificult for her/him to prevent the code from 
incurring into situations that lead the program to an unpredictable state. 
}
\end{minipage}}

>>>>

\noindent \fbox{ \begin{minipage}{0.96\columnwidth} \emph{
The study revealed: approximately 52\% of the reported stack traces were associated to programming mistakes;
and 27,71\% of all stack traces of reported a java.lang.NullPointerException the root cause.
}
\end{minipage}}

@@

\noindent \fbox{ \begin{minipage}{0.96\columnwidth} \emph{
The study revealed: an unexpected fragility - a checked exception being thown by a native method and not declared  
on the ``exception interface" of such method and all methods on the invocation chain.
}
\end{minipage}}

@@

\noindent \fbox{ \begin{minipage}{0.96\columnwidth} \emph{
The cross-type wrappings is an indication that even if the developer sticks to Java
specification and best practices, it will be dificult for her/him to prevent the code from 
incurring into situations that lead the program to an unpredictable state.
}
\end{minipage}}
